---
title: "DDS Case Study"
author: "Shravan Reddy"
date: "2/25/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
breweries <- read.csv(file="~/Desktop/DDS/CaseStudy1/Breweries.csv", header = TRUE)
beers <- read.csv(file="~/Desktop/DDS/CaseStudy1/Beers.csv", header = TRUE)
```

####1) How many breweries are present in each state?


```{r}
as.data.frame(table(breweries$State))
```

####2) Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.


```{r}
brewerybeer <- merge(breweries, beers, by.x = c("Brew_ID"), by.y = c("Brewery_id"))
head(brewerybeer,6)
tail(brewerybeer,6)
```

####3) Report the number of NA’s in each column.


```{r}
sapply(brewerybeer, function(x) sum(is.na(x)))
#apply(is.na(brewerybeer),2,sum)
#colSums(is.na(brewerybeer))
```

####4) Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.


```{r}
library(dplyr)
library(ggplot2)
Statemedians <- brewerybeer %>%
  group_by(State) %>%
  summarize(medianABV = median(ABV, na.rm = TRUE), medianIBU = median(IBU, na.rm = TRUE))
ggplot(Statemedians,aes(x=State, y=medianABV)) + geom_bar(stat="identity")
ggplot(Statemedians,aes(x=State, y=medianIBU)) + geom_bar(stat="identity")
```

####5) a.Which state has the maximum alcoholic (ABV) beer?


```{r}
brewerybeer[which.max(brewerybeer$ABV),4]

```

####5) b.Which state has the most bitter (IBU) beer?


```{r}
brewerybeer[which.max(brewerybeer$IBU),4]
```

####6) Summary statistics for the ABV variable.


```{r}
summary(brewerybeer$ABV)
```

####7) Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.


```{r}
ggplot(brewerybeer, aes(x=brewerybeer$ABV, y=brewerybeer$IBU)) + geom_point() +   
  geom_text(data=subset(brewerybeer, ABV > .1),
            aes(x=ABV, y=IBU,label=Name.y),check_overlap = TRUE, vjust = 0, nudge_y = 1.2) +
  geom_text(data=subset(brewerybeer, IBU > 125),
            aes(x=ABV, y=IBU,label=Name.y),check_overlap = TRUE, hjust = 0, nudge_x = 0.001)
```

###Extras
####Wordcloud of beer styles

```{r}
library(wordcloud)
wordcloud(gsub(" ","",beers$Style), scale = c(3, 0.4), random.color=TRUE, rot.per=.3, colors=brewer.pal(8, "Dark2"))
```

####Plot brewery counts by state

```{r, eval=F, echo=T}
library(ggmap)
BreweryByState<- breweries %>% group_by(State) %>% summarize(count=n())
BreweryByState$lon <- geocode(gsub(" ","",BreweryByState$State))$lon
BreweryByState$lat <- geocode(gsub(" ","",BreweryByState$State))$lat

map_us <- get_map(location = "United States", zoom = 4, color = "color")
ggmap(map_us, legend = "bottomright", extent = "device") + 
geom_point(data = BreweryByState, aes(x = lon, y = lat, size = Count), colour = "red") + 
  geom_text(data = BreweryByState, aes(x = lon, y = lat, label = Count), colour = "black", size = 3)
```

####Plot cities with breweries

```{r, eval=F, echo=T}
library(ggmap)
BreweryByCity<- breweries %>% group_by(City) %>% summarize(count=n())
BreweryByCity$lon <- geocode(gsub(" ","",BreweryByCity$City))$lon
BreweryByCity$lat <- geocode(gsub(" ","",BreweryByCity$City))$lat

map_us <- get_map(location = "United States", zoom = 4, color = "color")
ggmap(map_us, legend = "bottomright", extent = "device") + 
  geom_point(data = BreweryByCity, aes(x = lon, y = lat), colour = "red")
```