---
title: "SReddy_DDSHW4"
author: "Shravan Reddy"
date: "2/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### FiveThirtyEight Data (30 points): Navigate on GitHub to https://github.com/rudeboybert/fivethirtyeight and read README.md. Seriously, it will include everything you need. 
#####Install the fivethirtyeight package.

```{r}
library(fivethirtyeight)
```

#####In the listing of Data sets in package 'fivethirtyeight,' assign the eighteenth data set to an object 'df.'

```{r}
data(package = "fivethirtyeight")
df <- college_recent_grads
```

#####Use a more detailed list of the data sets to write out the URL in a comment to the related news story.

```{r}
vignette("fivethirtyeight", package = "fivethirtyeight")

#"http://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/""
```


#####Using R command(s), give the dimensions and column names of this data frame.

```{r}
nrow(df)
ncol(df)
colnames(df)
```

###Data Summary (30 points): Use your newly assigned data frame for Question 2. 
#####Write an R command that gives you the column names of the data frame.  Right after that, write one that counts the number of columns but not rows.  Hint: The number should match one of your numbers in Question 1d for dimensions.

```{r}
colnames(df)
ncol(df)
```

#####Generate a count of each unique major_category in the data frame.  I recommend using libraries to help.  I have demonstrated one briefly in live-session.  To be clear, this should look like a matrix or data frame containing the major_category and the frequency it occurs in the dataset.  Assign it to major_count.

```{r}
library(MASS)
major_count <- table(df$major_category)
major_count
```

#####To make things easier to read, put par(las=2) before your plot to make the text perpendicular to the axis.  Make a barplot of major_count.  Make sure to label the title with something informative (check the vignette if you need), label the x and y axis, and make it any color other than grey.  Assign the major_category labels to their respective bar.  Flip the barplot horizontally so that bars extend to the right, not upward.  All of these options can be done in a single pass of barplot(). Note: It's okay if it's wider than the preview pane.

```{r}
barplot(major_count, main = "The Economic Guide To Picking A College Major", xlab = "Majors", ylab = "Counts", col = "blue",las=2, horiz=TRUE)
```

#####Write the fivethirtyeight data to a csv file.  Make sure that it does not have row labels.

```{r}
write.csv(df, "fivethirtyeight.csv", row.names=F)
```
